### 2014-11-10 docs/ms.Rmd
Fixed issues with compiling manuscript. Head conflict was still in file and cauing problems so I deleted this and everything compiles perfectly.

Most studies using visual models analysed their data using receptor noise models (`r vismod_type[3]` of `r sum(vismod_type)` studies) while others used hexagon (`r vismod_type[1]` studies) or tcs (`r vismod_type[4]` studies). Case specific models were used in `r vismod_type[2]` cases. Overall, `r round(prop_irrad, digits =2)`% reported the type of irradiance, `r round(prop_spvismod, digits = 2)`% the species used in their visual model and `r round(propvis_mod_param, digits = 2)`% made explicit mention of the parameters they used (i.e. cone densities, neural vs quantum catchs etc.) in their methods. The background used in visual models was reported `r round(prop_bkg, digits = 2)`% of the time. The type of visual noise authors assumed was reported in `r round(prop_noise, digits = 2)`% of the studies. In addition, explicit mention of the type of quantum catche (`r round(prop_qcatch, digits = 2)`%) or whether photoreceptor adaptation (`r round(prop_adap, digits = 2)`%) was accounted for in visual models was not common.

>>>>

Most studies using visual models analysed their data using receptor noise models (`r vismod_type[3]` of `r sum(vismod_type)` studies) while others used hexagon (`r vismod_type[1]` studies) or tcs (`r vismod_type[4]` studies). Case specific models were used in `r vismod_type[2]` cases. Overall, `r round(prop_irrad, digits =2)`% reported the type of irradiance, `r round(prop_spvismod, digits = 2)`% the species used in their visual model and `r round(propvis_mod_param, digits = 2)`% made explicit mention of the parameters they used (i.e. cone densities, neural vs quantum catchs etc.) in their methods. The background used in visual models was reported `r round(prop_bkg, digits = 2)`% of the time. The type of visual noise authors assumed was reported in `r round(prop_noise, digits = 2)`% of the studies. In addition, explicit mention of the type of quantum catche (`r round(prop_qcatch, digits = 2)`% of studies) or whether photoreceptor adaptation (`r round(prop_adap, digits = 2)`%) was accounted for in visual models was not common.
